### 2018-06-07 5_eval.tex
lots of changes on itmo template.

In both pictures, the writes are denoted with the left-directed arrow `\lstinline{<-}', and the functions \lstinline{load} and \lstinline{store} denote the type of the shared memory event.
The primary transitions that denote unconditional jumps or if-true-transitions are pictured with solid lines, and the alternative transitions that denote if-false-transitions are pictured with dotted lines.
The graphs contain a single source event and a single sink event represented by the grey triangles (in fact, the graph produced by \porthos[1] does not have sink and source nodes, but they were added to the picture for demonstrative purposes).
For clarity, all branching events, that in current example serve as the conditional events of loops, are highlighed with light-grey colour.

\begin{figure}[!h]
%
\begin{subfigure}[b]{.49\textwidth}\centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/PorthosC/t0.png}
  \hfill
  \caption{The compiled \xgraph{} of the function in Figure~\ref{ex:both-cf:ptsC}}
  \label{ex:both-cf:graph:ptsC}
\end{subfigure}
%
\begin{subfigure}[b]{.49\textwidth}\centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/Porthos/t0.png}
  \hfill
  \caption{The compiled AST of the function in Figure~\ref{ex:both-cf:pts1}}
  \label{ex:both-cf:graph:pts1}
\end{subfigure}
%
\caption{The control-flow graphs of the functions represented in Figure~\ref{ex:test-both-cf}}
\label{ex:test-both-pic}
\end{figure}

@@

\begin{figure}[!h]
\begin{lstlisting}
{
  int x = 1, *y;
}

void thread_0(int &x, int &y) {
  L0: x = 0;
  int r;
  while (x * (5 + 4 / 2) % 3 == 1) {
    if (x != 0) {
      goto L0; //backward jump
    }
    if (y > 6) {
      continue;
    }
    else if (++y > 7) {
      r = r + 10;
      break;
    }
    else {
      goto L1; //forward jump
    }
    r = 11;
  }
  y = x + 1;
  L1: x = r;
}

@@

\end{lstlisting}
\caption{Example: A litmus test in C with an arbitrary control-flow}
\label{ex:cfg-arbitrary}
\end{figure}

@@

\begin{figure}[t]
\begin{lstlisting}
{ int x = 0; int y = 0;}

@@

exists(x == 0 && y == 0)
\end{lstlisting}
\caption{SB litmus test for the Linux kernel memory model}
\label{ex:sb:kernel}
\end{figure}

>>>>

In both pictures, the writes are denoted with the left-directed arrow `\lstinline{<-}', and the functions \lstinline{load} and \lstinline{store} denote the type of the shared memory event.
The primary transitions that denote unconditional jumps or if-true-transitions are pictured with solid lines, and the alternative transitions that denote if-false-transitions are pictured with dotted lines.
The graphs contain a single source event and a single sink event represented by the dark-grey triangles (in fact, the graph produced by \porthos[1] does not have sink and source nodes, but they were added to the picture for demonstrative purposes).
For clarity, all branching events, that in current example serve as the conditional events of loops, are highlighed with light-grey colour.

\begin{figure}[!h]
%
\begin{subfigure}[b]{.49\textwidth}\centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/PorthosC/t0.png}
  \caption{The compiled \xgraph{} of the function in Figure~\ref{ex:both-cf:ptsC}}
  \label{ex:both-cf:graph:ptsC}
\end{subfigure}
%
\begin{subfigure}[b]{.49\textwidth}\centering	
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/Porthos/t0.png}
  \caption{The compiled AST of the function in Figure~\ref{ex:both-cf:pts1}}
  \label{ex:both-cf:graph:pts1}
\end{subfigure}
%
\caption{The control-flow graphs of the functions represented in Figure~\ref{ex:test-both-cf}}
\label{ex:test-both-pic}
\end{figure}

@@

\begin{figure}%[!h]
\centering
\begin{minipage}[t]{.5\textwidth}%for preventing overfull
\begin{lstlisting}[language=Java]
{
  int x = 1, *y; //initialisation
}

void thread_0(int &x, int &y) {
  L0: x = 0; //labelled statement
  int r;
  while (x * (5 + 4 / 2) % 3 == 1) {
    if (x != 0) {
      goto L0; //backward jump
    }
    if (y > 6) {
      continue; //jump to the loop entry
    }
    else if (++y > 7) {
      r = r + 10;
      break; //jump to the loop exit
    }
    else {
      goto L1; //forward jump
    }
    r = 11;
  }
  y = x + 1;
  L1: x = r; //labelled statement
}

@@

\end{lstlisting}
\end{minipage}
\caption{Example: A litmus test in C with an arbitrary control-flow}
\label{ex:cfg-arbitrary}
\end{figure}

@@

\begin{figure}%[t]
\centering
\begin{minipage}[t]{.49\textwidth}%for preventing overfull
\begin{lstlisting}
{ int x = 0; int y = 0;}

@@

exists(x == 0 && y == 0)
\end{lstlisting}
\end{minipage}
\caption{SB litmus test for the Linux kernel memory model}
\label{ex:sb:kernel}
\end{figure}

### 2018-06-07 90_summary.tex
lots of changes on itmo template.

During the work on this thesis, we solved the following engineering and scientific tasks:

@@

  \begin{enumerate}[leftmargin=\parindent,label=\alph*.]
  \item The first stumbling block in extension of the input language was the \porthos[1] program input parser, which performs the full semantic analysis of the program.
  Although it works for a small subset of the C language, the rich and expressive language such as C requires several stages of analysis before the compilation stage.
  To handle this, we implemented the processing units that analyse the AST of the program on the \textit{pre-compilation} stage (see Section~\ref{ch:impl:proc:x-pre-compiler}).

  As an example, the \textit{variable kind analysis} (shared or local) is performed by \porthos[1] syntactically, depending on the operator or the function that uses the variable.
  In contrast, \porthos[2] traverses the program AST and collects information of all variables accessed in the program during the pre-compilation stage (see Section~\ref{ch:impl:proc:x-pre-compiler}).
  Currently, \porthos[2] considers a variable to be shared if it was declared as a pointer, or its address is accessed at least once by the code of any process, or it was declared as a parameter of the function that defines a process, or it was exported by \texttt{extern} keyword or an exporting function.

@@

>>>>

During the work on this thesis, we solved the following research and engineering problems:

@@

  \begin{enumerate}[label=\alph*.]
  \item The first stumbling block in extension of the input language was the \porthos[1] program input parser, which performs the full semantic analysis of the program.
  Although it works for a small subset of the C language, the rich and expressive language such as C requires several stages of analysis before the compilation stage.
  To handle this, we implemented the processing units that analyse the AST of the program on the \textit{pre-compilation} stage (see Section~\ref{ch:impl:proc:x-pre-compiler}).

  As an example, the \textit{variable kind analysis} (determining whether they are shared or local) is performed by \porthos[1] syntactically, depending on the operator or the function that uses the variable.
  In contrast, \porthos[2] traverses the program AST and collects information of all variables accessed in the program during the pre-compilation stage (see Section~\ref{ch:impl:proc:x-pre-compiler}).
  Currently, \porthos[2] considers a variable to be shared if it was declared as a pointer, or its address is accessed at least once by the code of any process, or it was declared as a parameter of the function that defines a process, or it was exported by \texttt{extern} keyword or an exporting function.

@@

\ifdefined\IsAalto
\else
  \vspace*{1em}
\fi
